---
title: "initial_models_margin"
output: html_document
---

now we are considering using margin as the response variable, but we are slightly concerned about the distribution, as it looks almost bimodal rather than normal, with a dip at zero

```{r}
lax %>%
  ggplot(aes(x = margin)) +
  geom_histogram(bins = 25) +
  theme_bw()
```

so now to try modeling it...

```{r}
takeawaymodel <- lm(margin ~ caused_turnover_gp, data = lax)

summary(takeawaymodel)
```
what about the diagnostic plots?
```{r}
autoplot(takeawaymodel)
```
the residuals vs fits looks like it has just a bit of curvature left over, so I should look at the scatterplot

```{r}
lax %>%
  ggplot(aes(x = caused_turnover_gp, y = margin)) +
  geom_point() +
  theme_bw()

```
there could be some curvature there I guess, so I'll try fitting a quadratic model...

```{r}
takeawaymodel2 <- lm(margin ~ caused_turnover_gp + 
                       I(caused_turnover_gp^2), data = lax)

summary(takeawaymodel2)

```
interesting, so both the linear term and the quadratic term were significant! now to look at the residual plots...
```{r}
autoplot(takeawaymodel2)
```
so it seemed to fix the curvature, but there is now an issue with non-constant variance in that residuals vs fitted values plot...

does the curvature issue pop up with all predictors?

```{r}
groundballmodel <- lm(margin ~ ground_balls_gp, data = lax)
summary(groundballmodel)

```

and the plots...
```{r}
autoplot(groundballmodel)
```
it's weird, because if I saw that residuals vs fits plot without the trendline thing, I would be happy with it, but the trendline is totally throwing me off...
